PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
finished RAMP COVID prediction model

++KT: Needs to be developed further for RAMP dataset
COVID prediction model for COPING
The COVID prediction model has coded the sexes opposite to our data set
```{r create numeric sex variable with male=1}

dat.coping <- dat.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Sex == "Male",
        true = 1,
        false = 0
      )
  )
```

@@

```{r COVID prediction model}
# linear model of covid symptoms
dat.coping <- dat.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex_respiratory) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

@@

## looking at cases over 0.5
freq(dat.coping$covid_odds_ratio_50, 
     cumul = FALSE) 
```

>>>>

The COVID prediction model has coded the sexes opposite to our data set
```{r create numeric sex variable with male=1}
if(GLAD == TRUE | NBR == TRUE | EDGI == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Sex == "Male",
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )
}
```

Sex is no available in the RAMP dataset, therefore a proxy sex variable is created whereby Gender = Male and Transgender = No. 
```{r create numeric sex variable with male=1 for ramp}
if(RAMP == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Gender == "Male" &
        Transgender_uncleaned == "No",
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )
}
```

Age is not available in RAMP, only categorical age. We will assign each individual the middle value of each age category. 
```{r create age - proxy variable for ramp}
if(RAMP == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Age =
      case_when(
        age_category_full == "16-18" ~ 17,
        age_category_full == "19-25" ~ 22,
        age_category_full == "26-35" ~ 30.5,
        age_category_full == "36-45" ~ 40.5,
        age_category_full == "46-55" ~ 50.5,
        age_category_full == "56-65" ~ 60.5,
        age_category_full == "66-70" ~ 68,
        age_category_full == "71-75" ~ 73,
        age_category_full == "76-80" ~ 78,
        age_category_full == "81-85" ~ 83,
        age_category_full == "86-90" ~ 88,
        age_category_full == "91-100" ~ 93,
      age_category_full == "100+" ~ 100
      )
  )
}
```

@@

#COVID prediction model
```{r COVID prediction model}
# linear model of covid symptoms
dat.coping <- dat.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex_respiratory) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

@@

## looking at cases over 0.5
freq(dat.coping$covid_odds_ratio_50, 
     cumul = FALSE)
